### 2025-12-10 Paper/paper_2025.tex

>>>>

    \appendix

% First part of the figure (page 1)
\begin{figure}[p] % 'p' places figure on a dedicated float page
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/bed_conc_graph.pdf}
        \caption{Bed Concentration}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/tot_discharges_graph.pdf}
        \caption{Total Discharges}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/perc_patients_graphs.pdf}
        \caption{Patient Type Proportions}
    \end{subfigure}

    \caption{ }
\end{figure}

% Second part of the figure (page 2)
\begin{figure}[p]
    \ContinuedFloat % continues numbering from previous figure
    \centering
    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/tot_oper_exp_graph.pdf}
        \caption{Operating Expenses}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/purchases_graphs.pdf}
        \caption{Purchases}
    \end{subfigure}

    \begin{subfigure}{\textwidth}
        \centering
        \includegraphics[width=0.8\textwidth]{Objects/pat_rev_graph.pdf}
        \caption{Patient Revenue}
    \end{subfigure}

    \caption{ }
\end{figure}
